%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Qiao Wang} % Your name
%\address{Room NO.1509, Building A, Nanyuanfengye Apartment, Nanshan Road, Nanshan District 51800Shenzhen, Guangdong, China} % Your secondary addess (optional)
%\address{+86-132-4671-5164 \\ wq120168196@yahoo.com} % Your phone number and email

\begin{document}
	
\begin{rSection}{Contact\\Information}
\textit{Address:} Room 1509, Building A, Nanyuanfengye Apartment, Nanshan Road\\
Nanshan District 51800 Shenzhen, Guangdong, China\\
\textit{Mobile:} +86-132-4671-5164\\
\textit{E-mail:} wq120168196@yahoo.com
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Sichuan University}, Chengdu, Sichuan, China \hfill {(Among top 20 universities in China)} \\ 
B.S. in Computer Science \hfill {\em July 2013} \\
Overall GPA: 3.12

\end{rSection}

\begin{rSection}{Working experience}
	{\bf Shenzhen Fecocyan Science Technology Co., Ltd},\\
	Project Manager  \hfill {\em October 2015 - present}\\*	
	{\bf TP-Link Technologies Co., Ltd.}, \hfill {(Global supplier of networking products)} \\
	Software Engineer  \hfill {\em July 2013 - June 2015}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Project}
	
\begin{rSubsection}{Development of TCP/IP Protocol Stack}{August 2016 - present}{Project Manager}{Shenzhen Fecocyan Science Technology Co., Ltd}
	\item Design the functional modules to implement TCP/IP protocol stack used in microcontroller.
	\item Develop the functional modules.
	\item Manage the project.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Bleasant Installed Box}{October 2015 - June 2016}{Project Manager}{Shenzhen Fecocyan Science Technology Co., Ltd}
	\item Designed and built all the functional modules to provide the solution of advertisement and application distribution through router.
	\item Developed functional modules of router.
	\item Fixed bugs of the wireless driver.
	\item Managed the project.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{D9-TT Modem Router}{February 2015 - June 2015}{Software Developer}{TP-Link Technologies Co., Ltd.}
	\item Fully implemented TR143 protocol.
	\item Test the performance of original SDK.
	\item Fixed 52 bugs of original SDK.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{TD-8960 ADSL2+ Modem Router}{July 2014 - October 2014}{Software Developer}{TP-Link Technologies Co., Ltd.}
	\item Developed firewall and QoS functions of router.
	\item Developed PPTP and L2TP functions of router.
	\item Fixed 36 bugs of original SDK.
	\item Developed acceleration module of PPTP L2TP to improve throughput.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{MT7620 Hardware Module For Letv Box}{February 2014 - June 2014}{Software Developer}{TP-Link Technologies Co., Ltd.}
	\item Developed a Windows-based software for RF evaluation and validation during manufacturing.
	\item Communicated and cooperated with Mediatek(the supplier of chips) and Letv(the client) to solve problems during development.
	\item Solved problems during manufacturing.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{TP-LINK genie APP for Android}{August 2013 - October 2013}{Android Developer}{TP-Link Technologies Co., Ltd.}
\item Completed demand analysis, the outline design and detail design.
\item Designed the network protocol and the format of data package transmitted between router and mobile device.
\item Implemented functions of Wireless Setting, Network Map, Live Parental Controls, Guest Access, Traffic Control.
\item Wrote test cases.
\item Maintained and refined project.
\end{rSubsection}

%------------------------------------------------
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

%Computer Languages & C C++ \\
%Protocols & TCP/IP TR143 \\
%Databases & MySQL \\
%Programming & Linux kernel development,Linux driver development,  \\
%System & Linux 
%\end{tabular}
Familiar with Linux kernel development, Linux driver development\\
Familiar with Unix Network Programming\\
Good at Algorithm \\
Good command of C/C++ 

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
